---
title: Tri-State County Maps
author: Rafael Zayas
date: '2020-04-23'
slug: tri-state-county-maps
categories: []
tags:
  - cv
  - geo
draft: yes
---

I've never used any geospatial data or mapping in R, but I have admired the elegant examples online for a few years now.  Now that I find myself very interested in county-level data, it seems like a good time to try my hand at this.

```{r setup conda env, message=TRUE, include=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(warning = TRUE)
library(tidyverse, warn.conflicts = FALSE)
library("reticulate")
library("leaflet")
library("sp")
library("rgdal")
reticulate::use_condaenv(
  condaenv = "mtcv",
  conda="C:\\Users\\rafae\\Anaconda3\\Scripts\\conda.exe"
)
shp_file_path = fs::fs_path("C:\\Users\\rafae\\Code\\cvdata\\cvdata\\geo-data\\tl_2019_us_county")
shp_file_name = "tl_2019_us_county"
stopifnot(fs::is_dir(shp_file_path))
stopifnot(fs::is_file(shp_file_path / glue::glue("{shp_file_name}.shp")))


```


```{python}
from cvdata.sources import county_stats
county_stats = county_stats("Morris", "New Jersey")

```

```{r county_data}
# py$county_stats %>% head()
# trying this approach
counties <- rgdal::readOGR(shp_file_path, shp_file_name, GDAL1_integer64_policy = TRUE)
tri_states_full <- subset(counties, counties$STATEFP %in% c("09","34","36")) # c("34"))  # tri-state: 
tri_states <- rmapshaper::ms_simplify(tri_states_full)
leaflet(tri_states) %>%
  addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.5,
    fillColor = ~colorQuantile("YlOrRd", ALAND)(ALAND),
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE))
```

Sources/References used:    
+ [Census county shape data](https://www.census.gov/geographies/mapping-files/time-series/geo/carto-boundary-file.html)   
+ [Census tiger line files](https://www.census.gov/geographies/mapping-files/time-series/geo/tiger-line-file.html)
+ [leaflet package docs](https://rstudio.github.io/leaflet/map_widget.html)    
+ [R Graph Gallery](https://www.r-graph-gallery.com/map.html)
+ [neonscience.org - helpful in understanding shapefiles](https://www.neonscience.org/dc-shapefile-attributes-r)
+ [SO answer re setting county boundaries](https://stackoverflow.com/a/56699861/3027540)
+ [SO answer for popups](https://stackoverflow.com/a/49212330/3027540)

